---
title: "Assignment 11"
author: "MJKelleher"
date: "March 26, 2018"
output:
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=TRUE}
rm(list=ls())

library(knitr)
library(ggplot2)
library(dplyr)
library(fpp)

dbxroot <- "https://dl.dropboxusercontent.com/spa/afq05cp80hp4ezn/downloads/public/msds-data/"
```

```{r, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
#
# This imports the R scripts, but does not execute them yet.
# They are executed later in the next code chunk
read_chunk('code/q01_a.R')
read_chunk('code/q01_b.R')
read_chunk('code/q01_c.R')
read_chunk('code/q02_a.R')
read_chunk('code/q02_b.R')
read_chunk('code/q02_c.R')
read_chunk('code/q02_d.R')

```

## 1) Warm Up: Brief Financial Data
### (a.) Investigate the DAX Index from the EuStockMarkets Object built into R.  Use only the DAX index.
```{r}
<<q01_a>>
```
### (b.) Create a rudimentary plot in blue with properly labeled axes, and appropriate title.  Add vertical red line at 1997.
```{r}
<<q01_b>>
```
### (c.) Decompose the timeseries into its components, using a mul;tiplicative model.  Create plots for all decomposed components, blue lines and red divider at 1997.
```{r}
<<q01_c>>
```

## 2) Cleaning and New Features
### (a.) 
```{r}
<<q02_a>>
```
#### For every forw in the statesize Dataframe, all rows from the original Filtered Dataframe from #1c are included.  Because statesize has 50 rows, we have exactly `50*SizeOf(mh2015_filtered)` number of rows in the merged dataset.  My guess is that while both DF's have the State Data, because they are Factors and not character data, even though from a character data perspective there is a match, they are NOT a match because the Factors are Unique.
### (b.) Correct the data mismatch between the dataframe in #1c and the statesize dataframe, and merge.
```{r}
<<q02_b>>
```
### (c.) Calculate a new variable in your combined data.frame() which indicates the VA hospitals per thousand square miles.
```{r}
<<q02_c>>
```

### (d.) GGPlot with VA's per 1000 Square Miles by Region, sorted by Descending Bar Plot
#### I ran out of time trying to figure out how to do a legend.
```{r}
<<q02_d>>
```

### (e.1) What patterns do you see? 
#### A large portion of the total hospitals are contained in a few states.

### (e.2) By this metric, is there any region that seems relatively high for VA medical centers per thousand square miles?
#### The eastern seaboard seems to be high in the count of hospitals.

### (e.3) How about low? 
#### Total count per thousand is small west of a certain point, with the exception of a couple states.

### (e.4) Given these data, what advice might you give your boss before you start modeling (and why)?
#### There are some states that seem to be low, and I would double check the aggregate data to make sure the counts are correct.  or possibly make sure responses were not lost, or not reported.  If data is getting dropped, this would bias the model.


## [Upload to GitHub](https://github.com/allthebits/mjk-msds6306)
- Files for this homework (Unit 10) are in this folder: **homework/unit_10**
- [RMD File](https://github.com/allthebits/mjk-msds6306/blob/master/homework/unit_10/homework_submission.Rmd)
- [HTML Version of Assignment 10](http://htmlpreview.github.io/?https://raw.githubusercontent.com/allthebits/mjk-msds6306/master/homework/unit_10/homework_submission.html)  -  It's the same exact content as this page, except served from GitHub

