---
title: "Assignment 11"
author: "MJKelleher"
date: "March 26, 2018"
output:
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=TRUE}
rm(list=ls())

library(knitr)
library(ggplot2)
library(dplyr)
library(fpp2)
library(MuMIn)

dbxroot <- "https://dl.dropboxusercontent.com/spa/afq05cp80hp4ezn/downloads/public/msds-data/"
```

```{r, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
#
# This imports the R scripts, but does not execute them yet.
# They are executed later in the next code chunk
read_chunk('code/q01_a.R')
read_chunk('code/q01_b.R')
read_chunk('code/q01_c.R')
read_chunk('code/q02_a.R')
read_chunk('code/q02_b.R')
read_chunk('code/q02_c.R')
read_chunk('code/q02_d.R')
read_chunk('code/q03_a.R')

```

## 1) Warm Up: Brief Financial Data
### (a.) Investigate the DAX Index from the EuStockMarkets Object built into R.  Use only the DAX index.
```{r}
<<q01_a>>
```
### (b.) Create a rudimentary plot in blue with properly labeled axes, and appropriate title.  Add vertical red line at 1997.
```{r}
<<q01_b>>
```
### (c.) Decompose the timeseries into its components, using a mul;tiplicative model.  Create plots for all decomposed components, blue lines and red divider at 1997.
```{r}
<<q01_c>>
```

## 2) Temperature Data
### (a.) Using the maxtemp dataset granted by loading fpp2, there are maximum annual temperature data in Celsius. For more information, use help(maxtemp). To see what you’re looking at, execute the command in ‘Examples’ in the help document.
```{r}
<<q02_a>>
```

### (b.) We are only concerned with information after 1990. Please eliminate unwanted information or subset information we care about.
```{r}
<<q02_b>>
```

### (c.) Melbourne Prediction

#### Utilize SES to predict the next five years of maximum temperatures in Melbourne. Plot this information, including the prior information and the forecast. Add the predicted value line across 1990-present as a separate line, preferably blue. 

#### So, to review, you should have: (all on one axis.)

* your fit
* the predicted value line overlaying it (1990-present) in blue
* and a forecast 2017 through 2021
* ALSO:  Find the AICc of this fitted model. You will use that information later.

```{r}
<<q02_c>>
```

### (d.) Now use a damped Holt’s linear trend to also predict out five years. Make sure initial=“optimal.” As above, create a similar plot to 1C, but use the Holt fit instead.
```{r}
<<q02_d>>
```

### (e) Compare the AICc of the ses() and holt() models. Which model is better here?

Based on the info from [Wikipedia on AICc](https://en.wikipedia.org/wiki/Akaike_information_criterion), the one with the smaller value is the better fitting model.  Thus, the SES model is the better model.


## 2) The Wands Choose the Wizard
### (a.) Utilize the dygraphs library. Read in both Unit11TimeSeries_Ollivander and _Gregorovitch.csv as two different data frames. They do not have headers, so make sure you account for that. This is a time series of Wands sold over years.
```{r}
<<q03_a>>
```


## [Upload to GitHub](https://github.com/allthebits/mjk-msds6306)
- Files for this homework (Unit 10) are in this folder: **homework/unit_11**
- [RMD File](https://github.com/allthebits/mjk-msds6306/blob/master/homework/unit_11/homework_submission.Rmd)
- [HTML Version of Assignment 11](http://htmlpreview.github.io/?https://raw.githubusercontent.com/allthebits/mjk-msds6306/master/homework/unit_11/homework_submission.html)  -  It's the same exact content as this page, except served from GitHub

