---
title: "Assignment 11"
author: "MJKelleher"
date: "March 26, 2018"
output:
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=TRUE}
rm(list=ls())

library(knitr)
library(ggplot2)
library(dplyr)
library(fpp2)
library(MuMIn)
library(xts)
library(dygraphs)

dbxroot <- "https://dl.dropboxusercontent.com/spa/afq05cp80hp4ezn/downloads/public/msds-data/"
```

```{r, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
#
# This imports the R scripts, but does not execute them yet.
# They are executed later in the next code chunk
read_chunk('code/q01_a.R')
read_chunk('code/q01_b.R')
read_chunk('code/q01_c.R')
read_chunk('code/q02_a.R')
read_chunk('code/q02_b.R')
read_chunk('code/q02_c.R')
read_chunk('code/q02_d.R')
read_chunk('code/q03_a.R')
read_chunk('code/q03_b.R')
read_chunk('code/q03_c.R')
read_chunk('code/q03_d.R')

```

## 1) Warm Up: Brief Financial Data
### (a.) Investigate the DAX Index from the EuStockMarkets Object built into R.  Use only the DAX index.
```{r}
<<q01_a>>
```
### (b.) Create a rudimentary plot in blue with properly labeled axes, and appropriate title.  Add vertical red line at 1997.
```{r}
<<q01_b>>
```
### (c.) Decompose the timeseries into its components, using a mul;tiplicative model.  Create plots for all decomposed components, blue lines and red divider at 1997.
```{r}
<<q01_c>>
```

## 2) Temperature Data
### (a.) Using the maxtemp dataset granted by loading fpp2, there are maximum annual temperature data in Celsius. For more information, use help(maxtemp). To see what you’re looking at, execute the command in ‘Examples’ in the help document.
```{r}
<<q02_a>>
```

### (b.) We are only concerned with information after 1990. Please eliminate unwanted information or subset information we care about.
```{r}
<<q02_b>>
```

### (c.) Melbourne Prediction

#### Utilize SES to predict the next five years of maximum temperatures in Melbourne. Plot this information, including the prior information and the forecast. Add the predicted value line across 1990-present as a separate line, preferably blue. 

#### So, to review, you should have: (all on one axis.)

* your fit
* the predicted value line overlaying it (1990-present) in blue
* and a forecast 2017 through 2021
* ALSO:  Find the AICc of this fitted model. You will use that information later.

```{r}
<<q02_c>>
```

### (d.) Now use a damped Holt’s linear trend to also predict out five years. Make sure initial=“optimal.” As above, create a similar plot to 1C, but use the Holt fit instead.
```{r}
<<q02_d>>
```

### (e) Compare the AICc of the ses() and holt() models. Which model is better here?

Based on the info from [Wikipedia on AICc](https://en.wikipedia.org/wiki/Akaike_information_criterion), the one with the smaller value is the better fitting model.  Thus, the SES model is the better model.


## 3) The Wands Choose the Wizard
### (a.) Utilize the dygraphs library. Read in both Unit11TimeSeries_Ollivander and _Gregorovitch.csv as two different data frames. They do not have headers, so make sure you account for that. This is a time series of Wands sold over years.
```{r}
<<q03_a>>
```

### (b.) You don’t have your information in the proper format! In both data sets, you’ll need to first convert the date-like variable to an actual Date class
```{r}
<<q03_b>>
```

### (c.) Use the library xts (and the xts() function in it) to make each data frame an xts object (effectively, a time series). You’ll want to order.by the Date variable.
```{r}
<<q03_c>>
```

### (d.) Bind the two xts objects together and create a dygraph from it.

* Give an effective title and x/y axes.
* Label each Series (via dySeries) to be the appropriate wand-maker. So, one line should create a label for Ollivander and the other for Gregorovitch.
* Stack this graph and modify the two lines to be different colors (and not the default ones!) Any colors are fine, but make sure they’re visible and that Ollivander is a different color than Gregorovitch.
* Activate a range selector and make it big enough to view.
* Use dyShading to illuminate approximately when Voldemort was revived and at-large: between 1995 to 1999.
* Enable Highlighting on the graph, so mousing over a line bolds it.

```{r}
<<q03_d>>
```

## [Upload to GitHub](https://github.com/allthebits/mjk-msds6306)
- Files for this homework (Unit 10) are in this folder: **homework/unit_11**
- [RMD File](https://github.com/allthebits/mjk-msds6306/blob/master/homework/unit_11/homework_submission.Rmd)
- [HTML Version of Assignment 11](http://htmlpreview.github.io/?https://raw.githubusercontent.com/allthebits/mjk-msds6306/master/homework/unit_11/homework_submission.html)  -  It's the same exact content as this page, except served from GitHub

