---
title: "Assignment 5"
author: "MJKelleher"
date: "February 11, 2018"
output: html_document
---

```{r setup, include=FALSE, echo=TRUE}
    # Clean the workspace, remove all existing Objects
    rm(list=ls())
```
1. GitHub Cloning
    + (a.) Import 2016 and assign column names
    ```{r}
    dbxroot <- "https://dl.dropboxusercontent.com/spa/afq05cp80hp4ezn/downloads/public/msds-data/";
    yob2016_url <- paste(dbxroot, "yob2016.txt", sep="");
    df <- read.csv(url(yob2016_url), stringsAsFactors=FALSE, sep=";", header=FALSE);
    names(df) <- c("FirstName", "Gender", "CountWithThisName")
    ```
    + (b.) Summary and structure of data
    ```{r}
    head(df)
    str(df)
    ```
    + (c.) Find name that ends with 3 y's
    ```{r}
    library(stringi)

    getReversedStartsWith <- function(val, regex){
        newval <- stringi::stri_reverse(val)
        newval <- grep(regex, newval, value = TRUE)
    }
    
    # Reverse all of the firstNames that match the regex, NA or empty String returned with no match
    reversed_y <- lapply(df$FirstName, function(x){ getReversedStartsWith(x, "^yyy") })
    # Remove all of the elements that are empty
    reversed_y <- reversed_y[lapply(reversed_y,length)>0]
    # Reverse the Strings back to the original spelling
    reversed_y <- lapply(reversed_y,stringi::stri_reverse)
    reversed_y
    ```
    + (c.) Remove this observation, save as new dataframe
    ```{r}
    # Find the row index of the name we found
    ndx <- which(df$FirstName == reversed_y[1], arr.ind=TRUE)
    sprintf("Found name %s at row index %d", df[ndx[1],]$FirstName, ndx[1])

    # Remove the row of the name we found
    y2016 <- df[-c(ndx[1]),]
    sprintf("Rows in original dataset: %d,  Rows in dataset with name removed: %d", nrow(df), nrow(y2016))

    # Make sure this name does not exist in the new dataset
    crosscheck <- lapply(y2016$FirstName, function(x){ getReversedStartsWith(x, "^yyy") })
    crosscheck <- crosscheck[lapply(crosscheck,length)>0]
    sprintf("Crosscheck of removing name %s, size of found is: %d", df[ndx[1],]$FirstName, length(crosscheck))
    ```
1. Data Merging
    + (a.) Import 2015 dataset assign column names
    ```{r}
    yob2015_url <- paste(dbxroot, "yob2015.txt", sep="");
    y2015 <- read.csv(url(yob2015_url), stringsAsFactors=FALSE, sep=",", header=FALSE);
    names(y2015) <- c("FirstName", "Gender", "CountWithThisName")
    head(y2015)
    str(y2015)
    ```
    + (b1.) Display last 10 rows, describe interesting observation of this data
    ```{r}
    tail(y2015, 10)
    ```
    + (b2.) Interesting observation about last 10 rows of Data
        + There are exactly 5 children with these names, and they all happen to be boys.
    + (c.) Merge 2016, 2016 on Name, drop All rows resulting in NA for either name count field
    ```{r}
    # Merge the 2 datasets, drop observations when there is not a match from either side
    #      and merge on FirstName and Gender
    final <- merge(y2016, y2015, all=FALSE, by=c("FirstName","Gender"))
    xcnt <- sum(is.na(final$CountWithThisName.x))
    ycnt <- sum(is.na(final$CountWithThisName.y))
    sprintf("Validation after merge: Count of NA for 2016: %d, Count of NA for 2015", xcnt, ycnt)
    ```
1. Data Summary
    + (a.) New field summing count from 2016 and 2016 called Total, grand sum of Total
    ```{r}
    # Re-calculate the count field
    final$Total <- final$CountWithThisName.x + final$CountWithThisName.y
    # Uncomment if you want to drop the ".x" and ".y" synthetic fields
    #final <- final[,c("FirstName","Gender","CountWithThisName")]
    str(final)
    grandTotal <- sum(final$Total)
    sprintf("Total number of children given popular names: %d", grandTotal)
    ```
    + (b.) Sort by Total, top 10 popular names
    ```{r}
    # Sort by the 'Total' Field
    final <- final[with(final, order(Total, decreasing=TRUE)), ]
    head(final,10)
    ```
    + (c.) Omit boys, report top 10 popular Girl names
    ```{r}
    # Select Observations by Gender, then get the Top 10
    top10girls <- head(final[which(final$Gender == "F"),],10)
    top10girls$FirstName
    ```
    + (d.) Drop all columns except FirstName, Total, write to CSV
    ```{r}
    # Remove all columns except FirstName and Total
    top10girls <- top10girls[, names(top10girls) %in% c("FirstName", "Total")]
    top10girls

    # Save the data to a CSV
    filename <- "top10-girl-names-2015-2016.csv"
    write.csv(df, file = filename, row.names=TRUE)

    # List files in the current directory matching the given pattern
    list.files(pattern=".*.csv$")
    ```
1. [Upload to GitHub](https://github.com/allthebits/mjk-msds6306)
    + Files for this homework (Unit 5) are in this folder: **homework/unit_05**
    + [RMD File](https://github.com/allthebits/mjk-msds6306/blob/master/homework/unit_05/homework_submission.Rmd)
    + [Codebook](https://github.com/allthebits/mjk-msds6306/blob/master/homework/unit_05/Codebook.md)
