---
title: "Assignment 9"
author: "MJKelleher"
date: "March 04, 2018"
output:
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=TRUE}
# Clean the workspace, remove all existing Objects
rm(list=ls())
library(knitr)
library(XML)
library(ggplot2)
```
```{r, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
#
# This imports the R scripts, but does not execute them yet.
# They are executed later in the next code chunk
read_chunk('scrape.r')
read_chunk('clean_table.r')
read_chunk('plot.r')

```


## Harry Potter Cast
### (a.) [View the cast members for the movies, understand the structure of the HTMl/XML](http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1)
### (b.) Scrape the page, collecting all of the cast.
```{r}
url <- "http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1"
#
# If you use TRUE, the URL gets parsed as the actual content, not the contents of the URL#
html <- htmlParse(url, asText=FALSE)

cleanCharacterNames = function(x){
    clean <- xmlValue(x)
    clean <- gsub("\\n", " ", clean)
    clean <- gsub("[[:space:]]+", " ", clean)
    clean <- trimws(clean)
    clean
}

# Collect the Actor names
xpath <- "//table[@class='cast_list']//span[@itemprop='name']"
castNames <- xpathSApply(html, xpath, xmlValue)

# Collect the Character Names
xpath <- "//table[@class='cast_list']//td[@class='character']/div"
castCharacters <- xpathSApply(html, xpath, cleanCharacterNames)

# Cross Check the sizes of the 2 Vectors BEFORE creating the dataframe
if (length(castNames) == length(castCharacters)) {
    castdf <- data.frame(castNames, castCharacters)
    names(castdf) <- c("Actor", "Character")
} else {
    sprintf("Cast vector size is %d, Characters vector size is %d, and they DO NOT match", length(castNames), length(castCharacters))
}
```
### (c.) Clean up the Table
`
As a result of the way we collected the data from the HTML table, there are no blank rows, Mr. Warwick's column is correct, and the non-Actor/character row was not collected.
`
### (d.) Split the actors name into 2 columns, FirstName and SurName, keeping middle name in the FirstName field.
```{r}
FirstName <- sub("^(.*) [^ ]*$", "\\1", castNames,perl=TRUE)
SurName <- sub("^.* ([^ ]*)$", "\\1", castNames,perl=TRUE)

castdf <- data.frame(FirstName, SurName, castCharacters)
names(castdf) <- c("FirstName", "SurName", "Character")
```
### (e.) Print the first 10 Rows
```{r}
head(castdf,n=10)
```

    
## SportsBall
### (a.) Understand the structure of [ESPN San Antonio Spurs player stats page](http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs), and more specifically the Shooting Statistics table.
### (b.) Scrape the Shooting Statistics table
```{r}
<<scrape>>
```
### (c.) Clean up the table: one observation per row, no blank rows, the column names or the "Totals" row.  Additionally, split the "PLAYER" column into 2 columns: 1 for name, 1 for position.  Lastly, make sure each column uses the correct data type for its contents, numbers for the stats columns, etc.
```{r}
<<clean_table>>
```
### (d.) Colorful bar chart that shows the Field Goals Percentage Per Game for each person
```{r}
<<plot>>
```


## [Upload to GitHub](https://github.com/allthebits/mjk-msds6306)
- Files for this homework (Unit 5) are in this folder: **homework/unit_09**
- [RMD File](https://github.com/allthebits/mjk-msds6306/blob/master/homework/unit_09/homework_submission.Rmd)
- [HTML Version of Assignment 9](http://htmlpreview.github.io/?https://raw.githubusercontent.com/allthebits/mjk-msds6306/master/homework/unit_09/homework_submission.html)  -  It's the same exact content as this page, except served from GitHub

