---
title: "Assignment 4"
author: "MJKelleher"
date: "February 04, 2018"
output: html_document
---

```{r setup, include=FALSE, echo=TRUE}
```
1. FiveThirtyEight Data
`
    - Read [GitHub Repo](https://github.com/rudeboybert/fivethirtyeight)
    - Install Library:
        - install.packages("fivethirtyeight")
    - Assign 18th dataset to Object: df
    - Use a more detailed list of the data sets to write out the URL in a comment to the related news story.
    - Using R command(s), give the dimensions and column names of this data frame
`
```{r}
library(fivethirtyeight)
# To see a list of all data sets:
five38 <- data(package = "fivethirtyeight", verbose=TRUE)
items <- five38$results[,"Item"]
eighteenthName <- items[18]
eighteenth <- get(data(list=eighteenthName, package = "fivethirtyeight"))
df <- eighteenth
dataframeInfo <- function(dataframe){
    allnames <- "Column Names: "
    for (name in names(dataframe)) {
        allnames <- paste(allnames, name, sep="  ")
    }
    allnames <- cat(allnames, "\n")
    tmp <- sprintf("Dimensions: Rows = %d, Columns = %d", nrow(dataframe), ncol(dataframe))
    allnames <- cat(allnames, tmp, "\n")
}

dataframeInfo(df)
```
1. More R Commands
```{r}
names(df)
ncol(df)

t <- table(df$major_category)
major_count <- data.frame(t[1:length(t)])
names(major_count) <- c("major_category", "count")
par(las=2)
barplot(major_count$count, beside = TRUE, xlim = c(0, 35), horiz=TRUE)

filename <- paste0(eighteenthName, ".csv")
write.csv(df, file = filename, row.names=FALSE)
```
1. Codebook
- [MJKelleher's GitHub Class Repository](https://github.com/allthebits/mjk-msds6306)
1. Swirl Modules 15
